---
title: "Vendor Details" 
output:
  html_notebook: default
---
<style>
  .myTable td {
    padding: 10px;
    border-bottom: 1px solid black;
  }
</style>

```{r echo=FALSE, message=FALSE, error=FALSE, warning = FALSE}
library(dplyr)
library(knitr)
library(DT)
library(plotly)
```

Hi Elvin,

I'm not sure what question you are trying to answer, but here is a high-level overview of Mas Active. Which I believe is the parent brand. Correct me if I'm wrong. 

```{r echo=FALSE, message=FALSE, error=FALSE, warning = FALSE}
vendor_levels <- as.data.frame(levels(SOT_Master$Parent_Vendor))

```

```{r echo =FALSE, message=FALSE, error=FALSE, warning = FALSE}
vendor_sub <-  levels(SOT_Master$Parent_Vendor)[223]

```



Looking at the YTD data, the Unit breakdwon by category for Vendor: **`r vendor_sub`** is such:

```{r echo=FALSE}
gen_Vendor <- SOT_Master %>% filter(Parent_Vendor == vendor_sub) %>% 
  select(Parent_Vendor, Category, Units ) %>% 
  group_by(Parent_Vendor, Category) %>% 
  summarise("SOT_Units" = sum(Units)) %>% 
  arrange(desc(SOT_Units))
kable(gen_Vendor, "html", table.attr='class="myTable"', format.args = list(big.mark=","), caption = "YTD Units by Category and Vendor")
```


<br>
Assuming you are interested in December only. I filtered down the month and show the Units for the month of December.

```{r echo=FALSE}
gen_Vendor_Dec <- SOT_Master %>% filter(Parent_Vendor == vendor_sub, 
                                       FISCAL_YEAR==2016, 
                                       grepl("DEC", Fiscal_Month, ignore.case = TRUE)) %>% 
  select(Parent_Vendor, Category, Units ) %>% 
  group_by(Parent_Vendor, Category) %>% 
  summarise("SOT_Units" = sum(Units)) %>% 
    arrange(desc(SOT_Units))
kable(gen_Vendor_Dec, format = "html", table.attr='class="myTable"', format.args= list(big.mark = ","), caption = "Units by Category and Vendor for December")

```

<br>

##### **Lateness by Brand and Category:**

To add some depth, we can look at the "Lateness" by brand and Category as well. Not sure what question you are trying to ask, but hope this helps.  


```{r echo=FALSE}
gen_Vendor_Late <- SOT_Master %>% filter(Parent_Vendor == vendor_sub, 
                                       FISCAL_YEAR==2016, 
                                       grepl("DEC", Fiscal_Month, ignore.case = TRUE)) %>% 
  select(Parent_Vendor, Category, Units, ReportingBrand, Lateness ) %>% 
  group_by(Parent_Vendor, Category, ReportingBrand, Lateness) %>% 
  summarise("SOT_Units" = sum(Units)) %>% 
    arrange( desc(SOT_Units))
datatable(format(gen_Vendor_Late, big.mark = ","), extensions = 'Buttons', options = list(
  pageLength = 5,
  dom = 'Bflrtip',
  buttons = list(
  'colvis',
  list(
  extend = 'collection',
  buttons = c('csv', 'excel', 'pdf'),
  text = 'Download'
  )
  )), caption = "Lateness by Brand and Category for December")
```
<br>
```{r echo=FALSE, include = FALSE, warning= FALSE, message= FALSE, error=FALSE}
gen_Vendor_plot <- gen_Vendor_Late %>% 
  group_by(ReportingBrand, Lateness) %>% 
  summarise("Shipped Units" = sum(SOT_Units)) 

plot_ly(mas_plot, x = mas_plot$ReportingBrand, y = mas_plot$`Shipped Units`)
```

Or if you want to see the same thing for the YTD:


```{r echo=FALSE}
gen_Vendor_Late <-
  SOT_Master %>% filter(Parent_Vendor == vendor_sub) %>%
  select(Parent_Vendor, Category, Units, ReportingBrand, Lateness) %>%
  group_by(Parent_Vendor, Category, ReportingBrand, Lateness) %>%
  summarise("SOT_Units" = floor(sum(Units))) %>%
  arrange((desc(SOT_Units)))
  # kable(gen_Vendor_Late, "html", table.attr='class="myTable"',format.args= list(big.mark = ","), caption = "Lateness by Brand and Category for YTD")
  datatable(
  format(gen_Vendor_Late, big.mark = ","),
  options = list(
  pageLength = 5,
  dom = 'Bflrtip',
  buttons = list(
  'colvis',
  list(
  extend = 'collection',
  buttons = c('csv', 'excel', 'pdf'),
  text = 'Download'
  )
  ),
  caption = "Lateness by Brand and Category for YTD"
  ))
```
<br>

Also, If you are interested in the raw data, see below. Quite a lot of columns, so you need to use the scroll bar. Again, hope this helps. 

```{r eval = FALSE, echo=FALSE, message=FALSE, error=FALSE, warning = FALSE}
full_details <- SOT_Master %>% 
  filter(Parent_Vendor == vendor_sub, 
         FISCAL_YEAR==2016)

datatable(format(full_details, big.mark =","), extensions ='Buttons'  , options = list(pageLength = 20, dom = 'Bflrtip', scrollX = TRUE, buttons = 
                                                 list('colvis', list(
                                                   extend = 'collection',
                                                   buttons = c('csv', 'excel', 'pdf'),
                                                   text = 'Download'
                                                 ))))
```

