---
title: "Mas Active Details"
output:
  html_notebook: default
---
<style>
  .myTable td {
    padding: 10px;
    border-bottom: 1px solid black;
  }
</style>

```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE, warning = FALSE}
library(dplyr)
library(knitr)
library(DT)
```

Hi Elvin,

I'm not sure what question you are trying to answer, but here is a high-level overview of Mas Active. Which I believe is the parent brand. Correct me if I'm wrong. 



Looking at the YTD data, the Unit breakdwon by category is such:

```{r echo=FALSE}
Mas_Active <- SOT_Master %>% filter(Parent_Vendor == levels(Parent_Vendor)[223]) %>% 
  select(Parent_Vendor, Category, Units ) %>% 
  group_by(Parent_Vendor, Category) %>% 
  summarise("SOT_Units" = sum(Units)) %>% 
  arrange(desc(SOT_Units))
kable(Mas_Active, "html", table.attr='class="myTable"', format.args = list(big.mark=","), caption = "YTD Units by Category and Vendor")
```


<br>
Assuming you are interested in December only. I filtered down the month and show the Units for the month of December.

```{r echo=FALSE}
Mas_Active_Dec <- SOT_Master %>% filter(Parent_Vendor == levels(Parent_Vendor)[223], 
                                       FISCAL_YEAR==2016, 
                                       grepl("DEC", Fiscal_Month, ignore.case = TRUE)) %>% 
  select(Parent_Vendor, Category, Units ) %>% 
  group_by(Parent_Vendor, Category) %>% 
  summarise("SOT_Units" = sum(Units)) %>% 
    arrange(desc(SOT_Units))
kable(Mas_Active_Dec, format = "html", table.attr='class="myTable"', format.args= list(big.mark = ","), caption = "Units by Category and Vendor for December")

```

<br>

##### **Lateness by Brand and Category:**

To add some depth, we can look at the "Lateness" by brand and Category as well. Not sure what question you are trying to ask, but hope this helps.  


```{r echo=FALSE}
Mas_Active_Late <- SOT_Master %>% filter(Parent_Vendor == levels(Parent_Vendor)[223], 
                                       FISCAL_YEAR==2016, 
                                       grepl("DEC", Fiscal_Month, ignore.case = TRUE)) %>% 
  select(Parent_Vendor, Category, Units, ReportingBrand, Lateness ) %>% 
  group_by(Parent_Vendor, Category, ReportingBrand, Lateness) %>% 
  summarise("SOT_Units" = sum(Units)) %>% 
    arrange( desc(SOT_Units))
datatable(format(Mas_Active_Late, big.mark = ","), extensions = 'Buttons', options = list(pageLength = 5, dom = 'lfrtBip' , buttons = c('excel', 'pdf', 'csv') ), caption = "Lateness by Brand and Category for December")
```
<br>

Or if you want to see the same thing for the YTD:


```{r echo=FALSE}
Mas_Active_Late <- SOT_Master %>% filter(Parent_Vendor == levels(Parent_Vendor)[223]) %>% 
  select(Parent_Vendor, Category, Units, ReportingBrand, Lateness ) %>% 
  group_by(Parent_Vendor, Category, ReportingBrand, Lateness) %>% 
  summarise("SOT_Units" = floor(sum(Units))) %>% 
    arrange((desc(SOT_Units)))
# kable(Mas_Active_Late, "html", table.attr='class="myTable"',format.args= list(big.mark = ","), caption = "Lateness by Brand and Category for YTD")
datatable(format(Mas_Active_Late, big.mark = ","), options = list(pageLength = 5, dom = 'lfrtBip', buttons = c('excel', 'pdf', 'csv')), caption = "Lateness by Brand and Category for YTD" )
```
<br>

Also, If you are interested in the raw data, see below. Quite a lot of columns, so you need to use the scroll bar. Again, hope this helps. 

```{r echo=FALSE}
datatable(format(Mas_Intimates, big.mark =","), extensions ='Buttons'  , options = list(pageLength = 5, dom = 'lfrtBip', scrollX = TRUE, buttons = c('excel', 'csv')))
```

