---
title: Vendor Details - **`r vendor_sub`**
output:
  html_notebook: default
---
<style>
  .myTable td {
    padding: 10px;
    border-bottom: 1px solid black;
    align-items: center
  }
</style>

```{r echo=FALSE, message=FALSE, error=FALSE, warning = FALSE}
library(dplyr)
library(knitr)
library(DT)
library(plotly)
library(dygraphs)
```

Here is vendor specific informantion for Vendor: **`r vendor_sub`**.  
\newline


```{r echo=FALSE, message=FALSE, error=FALSE, warning = FALSE}
vendor_levels <- as.data.frame(levels(SOT_Master$Parent_Vendor))

```

```{r echo =FALSE, message=FALSE, error=FALSE, warning = FALSE}
vendor_sub <-  levels(SOT_Master$Parent_Vendor)[442]

```

```{r include=FALSE, echo=FALSE, message=FALSE, error=FALSE, warning = FALSE, fig.width=6}
lungDeaths <- cbind(mdeaths, fdeaths)
dygraph(lungDeaths) %>%
  dySeries("mdeaths", label = "Male") %>%
  dySeries("fdeaths", label = "Female") %>%
  dyOptions(stackedGraph = TRUE) %>%
  dyRangeSelector(height = 20)
```


```{r echo=FALSE, message=FALSE, error=FALSE, warning = FALSE}
Weekly_SOT <- SOT_Master %>% 
  filter(Parent_Vendor == vendor_sub) %>%
  subset(Contract_Ship_Cancel >= "2016-01-31" & Contract_Ship_Cancel<= "2017-01-28") %>% 
  group_by(Contract_Ship_Cancel) %>% 
  summarise("On Time Units" = sum(Units[Lateness=="OnTime"], na.rm = TRUE),
            "Late Units" = sum(Units[Lateness=="Late"], na.rm = TRUE),
            "SOT Performance" = sum(`On Time Units`, na.rm=TRUE)/ (`On Time Units` + `Late Units`)*100) %>% 
  select(Contract_Ship_Cancel, `SOT Performance`) %>% 
  arrange(Contract_Ship_Cancel) %>% 
  as.data.frame()
```

Shipped On Time Performance for **`r vendor_sub`** is shown for the given period `r min(Weekly_SOT$Contract_Ship_Cancel)` to `r max(Weekly_SOT$Contract_Ship_Cancel)`

```{r echo=FALSE, message=FALSE, error=FALSE, warning = FALSE, fig.width=7, fig.align='center'}
rownames(Weekly_SOT) <- Weekly_SOT$Contract_Ship_Cancel 
Weekly_SOT <- select(Weekly_SOT, `SOT Performance`)
Weekly_SOT <- as.xts(Weekly_SOT)
dygraph(Weekly_SOT) %>% 
  dySeries(label = "SOT %", name="SOT Performance") %>% 
  dyRangeSelector()

```

<br>

Looking at the YTD data, the Unit breakdwon by category for YTD is:

```{r echo=FALSE, fig.align='center'}
gen_Vendor <- SOT_Master %>% filter(Parent_Vendor == vendor_sub) %>% 
  select(Parent_Vendor, Category, Units ) %>% 
  group_by(Parent_Vendor, Category) %>% 
  summarise("SOT_Units" = sum(Units)) %>% 
  arrange(desc(SOT_Units))

kable(gen_Vendor, "html", table.attr='class="myTable"', format.args = list(big.mark=","), caption = "YTD Units by Category and Vendor")
```


<br>

```{r echo=FALSE}
gen_Vendor_Dec <- SOT_Master %>% filter(Parent_Vendor == vendor_sub, 
                                       FISCAL_YEAR==2016, 
                                       grepl("DEC", Fiscal_Month, ignore.case = TRUE)) %>% 
  select(Fiscal_Month, Parent_Vendor, Category, Units ) %>% 
  group_by(Fiscal_Month, Parent_Vendor, Category) %>% 
  summarise("SOT_Units" = sum(Units)) %>% 
    arrange(desc(SOT_Units))
```

Looking only at the month of: **`r gen_Vendor_Dec$Fiscal_Month[1]`**

```{r echo=FALSE, fig.align='center'}
kable(gen_Vendor_Dec, format = "html", table.attr='class="myTable"', format.args= list(big.mark = ","), caption = "Units by Category and Vendor for December")

```

<br>

##### **Lateness by Brand and Category:**

To add some depth, we can look at the "Lateness" by brand and Category as well. Not sure what question you are trying to ask, but hope this helps.  


```{r echo=FALSE}
gen_Vendor_Late <- SOT_Master %>% filter(Parent_Vendor == vendor_sub, 
                                       FISCAL_YEAR==2016, 
                                       grepl("DEC", Fiscal_Month, ignore.case = TRUE)) %>% 
  select(Parent_Vendor, Category, Units, ReportingBrand, Lateness ) %>% 
  group_by(Parent_Vendor, Category, ReportingBrand, Lateness) %>% 
  summarise("SOT_Units" = sum(Units)) %>% 
    arrange( desc(SOT_Units))
datatable(format(gen_Vendor_Late, big.mark = ","), extensions = 'Buttons', options = list(
  pageLength = 5,
  dom = 'Bflrtip',
  buttons = list(
  list(
  extend = 'collection',
  buttons = c('csv', 'excel', 'pdf'),
  text = 'Download'
  )
  )), caption = "Lateness by Brand and Category for December")
```
<br>
```{r echo=FALSE, include = FALSE, warning= FALSE, message= FALSE, error=FALSE}
gen_Vendor_plot <- gen_Vendor_Late %>% 
  group_by(ReportingBrand, Lateness) %>% 
  summarise("Shipped Units" = sum(SOT_Units)) 

plot_ly(gen_Vendor_plot, x = gen_Vendor_plot$ReportingBrand, y = gen_Vendor_plot$`Shipped Units`)
```

Or if you want to see the same thing for the YTD:


```{r echo=FALSE}
gen_Vendor_Late <-
  SOT_Master %>% filter(Parent_Vendor == vendor_sub) %>%
  select(Parent_Vendor, Category, Units, ReportingBrand, Lateness) %>%
  group_by(Parent_Vendor, Category, ReportingBrand, Lateness) %>%
  summarise("SOT_Units" = floor(sum(Units))) %>%
  arrange((desc(SOT_Units)))
  # kable(gen_Vendor_Late, "html", table.attr='class="myTable"',format.args= list(big.mark = ","), caption = "Lateness by Brand and Category for YTD")
  datatable(
  format(gen_Vendor_Late, big.mark = ","), extensions = 'Buttons', options = list(
  pageLength = 5,
  dom = 'Bflrtip',
  buttons = list(
  list(
  extend = 'collection',
  buttons = c('csv', 'excel', 'pdf'),
  text = 'Download'
  )
  )),
  caption = "Lateness by Brand and Category for YTD"
  )
```
<br>

Also, we can look at the raw data for the top 50 DPO's by Units. This is quite a lot of columns, so you need to use the scroll bar.

```{r echo=FALSE, message=FALSE, error=FALSE, warning = FALSE}
full_details <- SOT_Master %>%
  filter(Parent_Vendor == vendor_sub,
  FISCAL_YEAR == 2016) %>%
  arrange(desc(Units))
  
  datatable(
  format(head(full_details, n = 50), big.mark = ","),
  extensions = 'Buttons',
  options = list(
  pageLength = 5,
  dom = 'Bflrtip',
  scrollX = TRUE,
  buttons =
  list(
 'colvis',
  list(
  extend = 'collection',
  buttons = c('csv', 'excel', 'pdf'),
  text = 'Download'
  )
  )
  )
  )
```

